\protect A Web of Human Knowledge: Unravelling Wikipedia's First Link Network

### 2015-11-23 writeup/2015-11-wikipedia-network.tex
article popularity and traversal visits

\begin{figure*}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/top_1k_path_length.png}  
  \caption{
    \textbf{Path Length Distribution for Top 1k articles}
  }
  \label{fig:Top 1k Path Length Distribution}
\end{figure*}

@@

\end{figure*}
The highest ranking article by n-degree, or the number of direct first links, is 
"United States" with 80,249 direct first links. Other high-ranking articles
include foundational abstract concepts such as "village," "species,"; 
sports associations such as "American Football," "Association Football"; 
and developed nations such as "France," "Japan," "Russia," "Australia," and 
the "Netherlands."

"Philosophy" and other Philosophical concepts which hold many traversal visits,
do not appear near the top when ranked by n-degree. 
"Philosophy" has an n-degree of 581, with direct first links from articles about Philosophers and areas of Philosophy: "Existentialism and Humanism," "Predeterminism," "Synoptic Philosophy,"Qualia," "Dorothy Emmet," and "Christopher W. Morris."
While many articles accumulate at "Philosophy," the accumulation is not the 
result of many articles directly referencing "Philosophy." 
Instead, the accumulation of first links, as we argued in our 
discussion of traversal visits, flows towards Philosophy as the 
ultimate anchor when genralizing from specific articles towards broader notions.

@@

Philosophy is not only a stand out the number of traversal visits, but also by the number articles "Philosophy" funnels into
its cycle. Of any article, the number of traversal funnels Philosophy holds exceeds 
all others by at least two orders of magnitude.
Next to the contribution of the largest funnels, "Philosophy" is a singularity. 
In proportion, "Presentation" holds only $0.4\%$ next to the number of traversal feeds for "Philosophy".
The second contributor to the Philosophy cycle is "Reality", funneling in a mere $0.2\%$ of traversals visits in the cycle.
Nevertheless, the other high ranking funnels are remarkably topical, culturally and politically important ideas.  For example, "Health Care", a recently high-contested legislative topic appears high on the list---Google trends indicates an uncharacteristic spike in search frequency between August-2009 and February-2010.
Other high ranking articles include key historical events such as the "Cold War" or critical scarce resource with recent 
media discussion such as "Fossil Fuel".
This coincidence of recent relevance and traversal feed rank suggests the First Link Network measurably represents
meaningful relationships not only among ideas, but also to English-speaking society.

\red{TODO: add two regimes for power-law distribution}

@@

Using a recently released api, we compare the popularity of a page to our 
findings about the FLN. We measure popularity as the total number 
of page views in the english edition of Wikipedia in the month of 
October 2015 (the earliest full month for which the data is available). 
We find \dots

%========================Conclusion====================================

>>>>

@@

\end{figure*}
The highest ranking article by n-degree is 
"United States" with 80,249 direct first links. Other high-ranking articles
include foundational abstract concepts such as "village," "species,"; 
sports associations such as "American Football," "Association Football"; 
and developed nations such as "France," "Japan," "Russia," "Australia," and 
the "Netherlands."

"Philosophy" and other philosophical concepts with many traversal visits
are not high-ranking by n-degree.
"Philosophy" has an n-degree of 581, with direct first links from articles about Philosophers and areas of Philosophy: "Existentialism and Humanism," "Predeterminism," "Synoptic Philosophy,"Qualia," "Dorothy Emmet," and "Christopher W. Morris."
While many articles accumulate at "Philosophy," the accumulation is not the 
result of many articles directly referencing "Philosophy." 
Instead, the accumulation of first links, as we argued in our 
discussion of traversal visits, flows towards Philosophy as the 
ultimate anchor when genralizing from specific articles towards broader notions.

@@

Philosophy is not only a stand out the number of traversal visits, but also by the number articles "Philosophy" funnels into
its cycle. Of any article, the number of traversal funnels Philosophy holds exceeds 
all others by at least two orders of magnitude.
Next to the contribution of the largest funnels, "Philosophy" is a singularity. 
In proportion, "Presentation" holds only $0.4\%$ next to the number of traversal feeds for "Philosophy".
The second contributor to the Philosophy cycle is "Reality", funneling in a mere $0.2\%$ of traversals visits in the cycle.
Nevertheless, the other high ranking funnels are remarkably topical, culturally and politically important ideas.  For example, "Health Care", a recently high-contested legislative topic appears high on the list---Google trends indicates an uncharacteristic spike in search frequency between August-2009 and February-2010.
Other high ranking articles include key historical events such as the "Cold War" or critical scarce resource with recent 
media discussion such as "Fossil Fuel".
This coincidence of recent relevance and traversal feed rank suggests the First Link Network measurably represents
meaningful relationships not only among ideas, but also to English-speaking society. 
\begin{figure*}[tp!]
  \centering	
  \includegraphics[width=\textwidth]{graphics/funnels_distribution.png}
  \caption{
    \textbf{Distribution of Traversal Funnels}
  }
  \label{fig:Funnels Distribution}
\end{figure*}

\red{TODO: add discussion of distribution}

@@

Using a recently released api, we compare the popularity of a page to our 
findings about the FLN. We measure popularity as the total number 
of page views in the english edition of Wikipedia in the month of 
October 2015 (the earliest full month for which the data is available). 
We find the highest ranking 1000 articles by traversal visits have an average of
$70$ thousand page views in October with high variation: the standard deviation 
is $1.1$ million page views. 
The number of page views has a skewed distrubtion with $75\%$ of articles
reaching fewer than $73$ thousand page views in October.
The article for "United States" has the most page 
views of the highest ranking $1000$ articles by traversal visits with 
$1.4$ million views in October. The next most popular articles are 
"India," "World War II," and the "United Kingdom" each with $0.7-1.03$ million page views.

The "Philosophy" article despite outranking every article in traversal visits,
has only $240$ thousand page views in October compared to the $1.4$ million
page views "United States" has.
While "Philosophy" is not itself the most popular article, "Philosophy" serves as 
an accumulation points for the ideas. Wikipedia users do not login specificially
to read about "Philosophy," but the authors relate ideas to "Philosophy" 
by ultimately anchoring the flow of first links to "Philosophy."

\begin{figure*}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/views_visits.png}
  \caption{
    \textbf{Article Popularity (by page views) compared to Traversal Visits 
    for Highest ranking 1000 articles}
    We use the total number of page views provided by Wikipedia for the month
    of October 2015 to compare each article's popularity to traversal visits.
    While the most popular articles do not necessarily correspond to the articles
    with the highest number of traversal visits, the variation in popularity appears to decrease as the number of traversal visits increases.
  }
  \label{fig:Views and Visits}

\red{REDO analysis}
\begin{figure*}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/funnels_visits.png}
  \caption{
    \textbf{Article Popularity (by page views) compared to Traversal Funnels
    for Highest ranking 1000 articles}
  }
    We use the total number of page views provided by Wikipedia for the month
    of October 2015 to compare each article's popularity to traversal funnels.
  \label{fig:Views and Funnels}
\end{figure*}
%========================Conclusion====================================
